%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{multirow}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\color{black}
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{\color{blue}{#1}} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\mitSubheading}[2]{
	\vspace{-1pt}\item
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\textit{\small#1} & \textit{\small #2} \\
	\end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[label={},leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\Cambridge}{Cambridge, MA}
%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \multirow{2}{*}{\textbf{\huge Noam Buckman}} & \href{nbuckman@mit.edu}{nbuckman@mit.edu}\\
   & 248-302-4327 \\
\end{tabular*}
%Graduate researcher with passion for autonomous ground \& aerial vehicles and large multi-robot teams. Experience applying math and algorithmic skills to hard problems: dealing with real-complex systems in dynamic \& uncertain environments.  Very strong coding and building skills, applied to robotics hardware and simulations.

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
  	\resumeSubheading
     {Massachusetts Institute of Technology}{Cambridge, MA}  	
  	{Ph.D. in Mechanical Engineering (Robotics); Minor: Computer Science GPA: -/5.0}{Sep. 2018 -- present}
\resumeItemListStart      
\resumeItem{Awards}{National Defense Science and Engineering Graduate (NDSEG) Fellowship}      
\resumeItemListEnd        	
    \mitSubheading
%      {Massachusetts Institute of Technology}{Cambridge, MA}
      {M.S. in Mechanical Engineering (Robotics); GPA: 4.7/5.0}{Feb. 2016 -- Sep. 2018}      
      \resumeItemListStart
	      \resumeItem{Courses}{Autonomy \& Decision Making, Autonomous Vehicles, Estimation \& Learning, Information Theory}
	      \resumeItem{Thesis}{Decentralized Task Allocation for Dynamic, Time-Sensitive Tasks}
	  \resumeItemListEnd
    \mitSubheading
%      {Massachusetts Institute of Technology}{Cambridge, MA}
      {B.S. in Mathematics and Mechanical Engineering, Minor: Economics;  GPA: 4.8/5.0}{Aug. 2012 -- Feb. 2016}
    \resumeItemListStart
    \resumeItem{Courses}{Algorithms, Computation Structures, Discrete Applied Math, Nonlinear Dynamics, Product Design, }
    \resumeItem{Honors}{Tau Beta Pi Engineering Honor Society, Pi Tau Sigma Mechanical Engineering Honor Society}
    \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
	\resumeSubheading
	{Aurora Flight Sciences}{\Cambridge}
	{Autonomy Intern}{Summer 2018}
	\resumeItemListStart
	\resumeItem{Multivehicle Autonomous Coordination}
	{Developed and implemented planning algorithms for coordinating future network of air taxis in C++}
   \resumeItemListEnd
   
    \resumeSubheading
      {MIT Laboratory for Information \& Decision Systems}{\Cambridge}
      {Graduate Research Assistant, \textit{Adviser: Prof. Jonathan How}}{Sep 2016 - June 2018}
      \resumeItemListStart
        \resumeItem{Wireless Broadcasting for Robot Teams}
          {Studied effects of mesh communication on team-wide consensus using Raspberry Pi's (Presented at RSS 2018:  Real Communication in Wild Workshop)}
        \resumeItem{Decentralized Dynamic Task Allocation}
          {Created decentralized algorithm--CBBA with Partial Replanning-- that can allocate tasks online with provable convergence.  Convergence and optimality tested on homemade Python simulator and Raspberry Pi's.  (Accepted at AAAI Guidance, Navagation \& Control, Jan. 2019)}
      \resumeItemListEnd

    \resumeSubheading
      {Woobo, Inc.}{\Cambridge}
      {Hardware/Robotics Intern}{Summer 2016}
      \resumeItemListStart
        \resumeItem{Mechatronic Design}
          {Lead on electronics for interactive robotic companion, created custom circuits for I/O of the robot and mechanical actuation}
        \resumeItem{Electronics Software Integration}
          {Developed Java library to control multiple sensors, LEDs, and motors to communicate with Android app backbone using IOIO microcontroller}
      \resumeItemListEnd

    \resumeSubheading
      {MIT Department of Mechanical Engineering}{}
      {Teaching Assistant}{Feb. 2013 - July 2016 }
      %{Teaching Assistant}{April 2013 - July 2016 }
      \resumeItemListStart
        \resumeItem{Graduate Residential TA}
          {Held weekly office hours, prepared homework problems and quizzes on MITx (60 students)}
        \resumeItem{2.01x QA Team Manager, Discussion Moderator, Content Editor}
          {Managed team of undergraduate Quality Assurance team (3 MIT students) for online EdX course; Edited course material and moderated online discussion forums }
      \resumeItemListEnd

%    \resumeSubheading
%      {MIT Experimental Hydrodynamics Lab}{}
%      {Undergraduate Research Assistant, \textit{Adviser: Prof. Alex Techet}}{June 2015 - Dec 2015}
%      \resumeItemListStart
%        \resumeItem{Fish Impulse Model}
%          {Examined impulse model using OpenFoam CFD software, results presented at APS Division of Fluid Dynamics Conference}
%        \resumeItem{Computational Fluid Dynamics Simulations}
%          {Learned and wrote guide to OpenFoam, created synthetic datasets that can be used to validate experimental methods}
%      \resumeItemListEnd
      
    \resumeSubheading
	 {MIT Department of Mechanical Engineering}{}
      {Undergraduate Research Assistant, \textit{Adviser: Prof. Dick Yue}}{June 2014 - May 2015}
     \resumeItemListStart
     	\resumeItem{Autonomous Buoys for Persistent Surveillance}
	     {Designed, tested, and built buoy exterior design to minimize energy consumption, and implemented GPS sensor suite and motor controls with Adruino Mega.  Created Python GUI for multi-robot monitoring and communication with XBee modules for effective real-time deployment}
%		 \resumeItem{Mechanical Design \& Controls of Autonomous Buoy}
%	      {Designed, tested, and built buoy exterior design to minimize energy consumption, and implemented GPS sensor suite and motor controls with Adruino Mega}
%		 \resumeItem{Multi-robot Offboard Control and Communication}
%		  {Developed Python GUI for multi-robot monitoring and communication with XBee modules for effective real-time deployment}
    \resumeItemListEnd      

  \resumeSubHeadingListEnd
  
  \section{Technical Skills}
  \resumeSubHeadingListStart
   \resumeSubItem{Software} C++ (fluent), Python (fluent), Java (proficient), MATLAB (proficient), Linux, ROS, Git,  LaTeX
  \resumeSubItem{Mechanical}
  {SolidWorks, Arduino, Raspberry Pi, Electronics/Circuits, CFD, Machine Trained}
  \resumeSubHeadingListEnd

\section{Service and Leadership}
\resumeSubHeadingListStart
\resumeSubItem{MIT OpenCourseWare Faculty Advisory Committee}{Graduate, Undergraduate Member\hfill June 2015-present}
\resumeSubItem{MIT Presidential Committee on Future of OCW}{Member \hfill June 2016- Dec 2016}
\resumeSubItem{MIT Graduate Hillel}{Treasurer \hfill Nov 2016-present}
\resumeSubHeadingListEnd

%-----------PROJECTS-----------------


%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
